Gravitational wave sensitivity curves

### 2014-07-29 Typesofsource.tex
h_rss

An alternative method for graphically representing the sensitivity of a GW detector to stochastic backgrounds, called the \emph{power-law-integrated sensitivity curve}, was suggested by \cite{2013PhRvD..88l4032T}. This method accounts for the fact that there is power across all frequencies in the sensitivity band by integrating the noise weighted signaal over frequency. As our aim here is to present stochastic backgrounds alongside other types of sources for comparison we do not use this approach.

@@

As discussed in \ref{sec:insp}, the expected relation between $h_\mathrm{c}(f)$ and a typical waveform $\tilde{h}(f)$ is
\begin{equation}\label{eq:simple} 
h_\mathrm{c}(f) = \left|\tilde{h}(f)\right|\sqrt{{N}_{\mathrm{cycles}}} \; , 
\end{equation}
where ${N}_{\mathrm{cycles}}$ is the number of cycles of radiation generated by the source. For bursts, $N_{\mathrm{cycles}}$ is of order unity and $\tilde{h}(f)$ is strongly peaked around some central frequency.

>>>>

An alternative method for graphically representing the sensitivity of a GW detector to stochastic backgrounds, called the \emph{power-law-integrated sensitivity curve}, was suggested by \cite{2013PhRvD..88l4032T}. This method accounts for the fact that there is power across all frequencies in the sensitivity band by integrating the noise weighted signal over frequency. As our aim here is to present stochastic backgrounds alongside other types of sources for comparison we do not use this approach.

@@

As discussed in \ref{sec:insp}, the expected relation between $h_\mathrm{c}(f)$ and a typical waveform $\tilde{h}(f)$ is
\begin{equation}\label{eq:simple} 
h_\mathrm{c}(f) = \left|\tilde{h}(f)\right|\sqrt{{N}_{\mathrm{cycles}}} \; , 
\end{equation}
where ${N}_{\mathrm{cycles}}$ is the number of cycles of radiation generated by the source, which is of order unity for bursts. Due to the uncertainty of burst models, the waveform is commonly indicated by a constant amplitude across some finite bandwidth. This is analogous to computing the root-sum-square of the waveform polarisations
\begin{equation}
h_\mathrm{rss} = \sqrt{\int{|h_+(t)|}^2 + {|h_\times(t)|}^2\,\rmd t},
\end{equation}
which is a quantity that is used to characterise the sensitivity of detectors to bursts \citep{Bursts}. In this work, we favour a constant $h_\mathrm{c}(f)$ over $h_\mathrm{rss}$ for consistency with the other types of source.
